I recently came across your job posting for a front end Engineer in Iceland and it really caught my eye not just because the tech stack is literally what I usually pick for personal projects in the frontend but because of the idea of working on-site in iceland. Iceland has always been top of my list on my places-to-go list just because of how cozy and beautiful it is and the idea of working on site in Reykjavík with Top-notch coffe, an on-site gym and a world class hot tub really feels like a dream come true.

I am a passionate Full Stack Software Engineer with extensive experience in modern web technologies. Throughout my years as a software engineer, I taught myself to design my own UIs using figma and I would say I do have an eye for design. My main hobbie project is literally about building a better and more customized user experience from scratch for my unix operating systems while preserving an aesthetically pleasing UI.

Over the past three years, I've built sophisticated frontend solutions using React and Vue. I've also design complicated microservices architectures and developed lots of APIs both professionally and for personal projects. I have even worked with all the technologies (except Amazon SQS) you mentioned in the backend! I genuenly believe I am a good fit for this position and I would really love if we could schedule a meeting to validate this assumption.

I also really like the section about the job posting where you mentioned that in your company you focus on what matters and embrace a fast paced environment. Also, the idea of your engineers being 5+ years with Bókun despite knowing how lucrative and common is job hopping nowadays really speaks volumes about the company's culture and values.

Finally, I want to thank you for your consideration and taking the time to read my cover letter, I look forward to hearing from you soon.
